Computer Science House Constitution

### 2024-01-30 constitution.tex
Resolve #78 - change reslife to student development (#112)
* Fixed wording

* Changed student development to campus life

* Made requested changes

\asection{Derivation of Authority}
The Computer Science House shall recognize that it receives its right to function as a Special Interest House from the Center for Residence Life.

>>>>

\asection{Derivation of Authority}
The Computer Science House shall recognize that it receives its right to function as a Special Interest House from the Center for Campus Life and the Department of Residence Life.
